\documentclass[9pt]{style/developercv}

\edef \myLocation{\directlua{tex.sprint(os.getenv('LOCATION'))}}
\edef \myCellPhone{\directlua{tex.sprint(os.getenv('CELL_NUMBER'))}}
\edef \myEmailLink{\directlua{tex.sprint(os.getenv('EMAIL_LINK'))}}
\edef \myEmail{\directlua{tex.sprint(os.getenv('EMAIL_DISPLAY'))}}
\edef \myLinkedinLink{\directlua{tex.sprint(os.getenv('LINKEDIN_LINK'))}}
\edef \myLinkedin{\directlua{tex.sprint(os.getenv('LINKEDIN_DISPLAY'))}}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth}
	\vspace{-\baselineskip}

	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Michał}}}}}
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Suwara}}}}}
	
	\vspace{6pt}
	
	{\huge DevOps Engineer}
\end{minipage}
\begin{minipage}[t]{0.285\textwidth}
	\vspace{-\baselineskip}
	
	\icon{MapMarker}{10}{\myLocation}\\
	\icon{Phone}{10}{\myCellPhone} \\
	\icon{At}{10}{\href{\myEmailLink}{\myEmail}}\\	
\end{minipage}
\begin{minipage}[t]{0.285\textwidth}
	\vspace{-\baselineskip}
	
	\icon{Github}{10}{\href{https://github.com/pl-misuw}{MichalSuwara}}\\
	\icon{Linkedin}{10}{\href{\myLinkedinLink}{\myLinkedin}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{1\textwidth} % 80% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	I am an engineer with 5 years’ experience working in technology. Due to my work with consultancy agencies I have a strong understanding of processes, engineering principles and communication with clients and stakeholders.\\

	I have primarily worked on the Windows-related web stack, but have worked across a broad range of technologies thereon: Groovy, Linux, Docker and most recently Openshift and Kubernetes; as well as spending a reasonable amount of time building applications for the web, which has given me an exposure to a range of web-related skills (Graphic design, coding, services, workflows, AWS integrations). \\

\end{minipage}

\vspace{1cm}

%----------------------------------------------------------------------------------------
%	TOP QUALITIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}

	\cvsect{People person}

	I enjoy working with interesting people, with understanding of business-related topics, management and emphasis 
	on DevOps culture.
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}
	
	\cvsect{Ownership}
	
	When given a task, project or issue to solve, I always take full responsibility for the outcome - doing my upmost
	best to deliver solution, whilst fostering cooperative approach in development process.
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}
	
	\cvsect{Creativity}
	
	Throughout my career, I have been working of multitude of different creative tasks, from graphic design to DevOps-related duties.
	Always seeking the creative solutions to presented problems. 
\end{minipage}

\vspace{0.75cm}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
	    {2018 -- Present\\\footnotesize{DevOps Engineer}}
		{Nordea}
		{
			\texttt{Nix}\slashsep
			\texttt{Kubernetes/Openshift}\slashsep
			\texttt{Unix systems}\slashsep
			\texttt{Jenkins}\\

			Work with Openshift platform, containerization and applications deployments and maintanance. \\
			Work with clients and stakeholders in regards to migration and transition processes. This includes support in automation, containerization and run of apps. \\
			Work with Nix environment, both Nix package manager and NixOS \\
			Continuous Deployment pipelines based on Jenkins
		}
	\entry
		{2017 -- Mar\\\footnotesize{DevOps Engineer}}
		{Accenture}
		{
			\texttt{Jenkins}\slashsep
			\texttt{Windows Stack}\slashsep
			\texttt{Docker}\slashsep
			\texttt{AWS}\slashsep
			\texttt{Monitoring}\\
 
 			Deployment automation using Jenkins, Virtual Machines (Hyper-V) Powershell, Windows Server Core, Docker, NugetFeed and MSBuild Tools.\\ 
 			AWS configuration, administration and automation (EC2, S3, RDS)\\
 			Deploying and configuring the web app (CMS) used for the project.\\
			Troubleshooting problems related to Application performance stability and deployments.\\
			Troubleshooting VM's and VM administration.\\
			Troubleshooting Hardware issues (with on-site ardware)
		}
	\entry
		{2016 -- 2017\\\footnotesize{DevOps Engineer}}
		{ZeroChaos/ABB}
		{
			\texttt{Jenkins}\slashsep
			\texttt{Windows Stack}\slashsep
			\texttt{Docker}\slashsep
			\texttt{AWS}\slashsep
			\texttt{Monitoring}\\

			Work with TeamCity, Jenkins, Team Foundation Server, MSBuild, Windows server.\\
			Coding, automating deployment procedures. VCS software and Version Control management.\\
			Collaboration with Developers, QA and Business (stakeholders, product owners).\\
			Amazon Web Services – RDS, Console, EC2 route 53, s3 management.\\
			Monitoring and maintaining Application stability.
		}
	\entry
		{2014 -- 2016\\\footnotesize{Application Specialist}}
		{ZeroChaos}
		{
			\texttt{Bug/feature testing}\slashsep
			\texttt{Troubleshooting}\slashsep
			\texttt{Documentation}\slashsep
			\texttt{Front and Back-end related support duties}\slashsep
			\texttt{Monitoring}\\

			
			Diagnosingand resolving hardware and software problems. \\
			Communicating with third party technical specialists. \\
			Working with Development and Operations teams. \\
			Troubleshooting, feature testing, feature integration. \\
			Technical documentation, process descriptions. \\
			Maintaining application continuous availability. \\
			Bug tracking.
		}
	\entry
		{2013 -- 2014\\\footnotesize{IT SUPPORT}}
		{Eurocent S.A.}
		{
			\texttt{SQL databases}\slashsep
			\texttt{Support with office tools}\slashsep
			\texttt{Microsoft Domain administration}\slashsep
			\texttt{.NET MVC}\\

			Diagnosing and resolving hardware, software and end user problems. \\
			Acting as the first point of contact for all IT and technical queries. \\
			Working within TCP/IP network environment, including DHCP, DNS and Ethernet. \\
			Involved in the rollout of software and hardware updates. \\
			Communicating with third party technical specialists. \\
			Provide secondary support for LAN administration. \\
		}
	\entry
		{Sep 2011 -- Mar 2014\\\footnotesize{Graphic designer}}
		{IT4BUSINESS}
		{
			\texttt{Multitude of Design and motion graphics softrware}\slashsep
			\texttt{CSS}\slashsep
			\texttt{Bootstrap}\slashsep
			\texttt{JavaScript}\slashsep
			\texttt{Node.js}\\

			Worked as a website designer and backend developer - have written 
			couple of static websites (adhering to responsive design)\\
			The skills acquired mostly relate to designing a functional website, as 
			well as technicalities of web protocols.
		}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}

	\cvsect{Languages}

	\textbf{English} - proficient\\
	\textbf{Polish} - native
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}
	
	\cvsect{Hobbies}
	
	Role-playing games\\
	Visual arts\\
	History and historical reenactment\\
	Memes
\end{minipage}

%----------------------------------------------------------------------------------------

\vspace{1.00cm}

\begin{minipage}[t]{1\textwidth}
	I hereby agree to the processing of personal data provided in this document for 
	realising the recruitment process pursuant to the Personal Data Protection Act
	of 10 May 2018 (Journal of Laws 2018, item 1000) and in agreement with Regulation (EU) 
	2016/679 of the European Parliament and of the Council of 27 April 2016 on the 
	protection of natural persons with regard to the processing of personal data and on 
	the free movement of such data, and repealing Directive 95/46/EC (General Data 
	Protection Regulation).
\end{minipage}

\end{document}
